Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-02-12 Multiresolution_framework/ltx/manuscript.tex
edit to the appendix

\section{Lower bound}\label{ap:QDerivation}

@@

The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the RTS smoother outputs (see \ref{ap:Xiderivation} for more details)

@@

where each $ 1 \times n_{\theta}$ block of the $n_x \times n_x n_{\theta}$ block matrix $\mathbf U$ is 
\begin{align}\label{eq:app-Uij}
\left[ \mathbf U\right] ^{k,i}&=\int_{\boldsymbol \Omega}\left[\boldsymbol\mu(r) \right]_k \left[\int_{\boldsymbol\Omega} \boldsymbol\mu\left(r'\right)\boldsymbol \lambda^\top \left(r-r'\right) \mathrm{d}r'\right]_{i:} \mathrm{d}r,
By substituting for $\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}$ from Eq.~\eqref{eq:app-LambdaThetaElements} the trace given in Eq.~\eqref{eq:MRA-trace1} can be written as

>>>>

\section{Construction and maximization of the Lower bound for the state-space representation of the MRAIDE}\label{ap:QDerivation}

@@

The matrices $\boldsymbol\Xi_0$ and $\boldsymbol\Xi_1$ are calculated using the RTS smoother outputs (see \ref{ap:Xiderivation} for more details).

@@

where $\left[ \mathbf U\right] ^{k,i}$ can be computed using Eq.~\eqref{eq:Uij}. By substituting for $\left[ \boldsymbol\Lambda_{\theta}\right] _{k,i}$ from Eq.~\eqref{eq:LambdaThetaElements} the trace given in Eq.~\eqref{eq:MRA-trace1} can be written as
